Title

### 2023-06-14 main.tex
Ediciones

>>>>

\tbnote{O algo como lo siguiente:}

{\color{purple}
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps.
We observed that the fidelity of 
simulating Pauli channels on one of IBM's quantum computers
was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
which was attributed to the current limitations of quantum computers.
Additionally, when working with Pauli dynamical maps,
we determined in theorem \ref{theorem2} the general mathematical conditions
under which a parametrized quantum circuit requires only one single-qubuit rotation dependent on the parameter.

Therefore, this work presents another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we find the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
can be used for any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.
}
